---
title: "Edgar Anderson's Irises"
bibliography: bibliography.bib
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.align = "center")
knitr::opts_chunk$set(fig.height = 4)
knitr::opts_chunk$set(fig.width = 10)
```



This data set consistst of four continuous characters collected for three species of *Iris*.
The data were assembled by Anderson [-@anderson1935irises] and famously analysed by Fisher [-@fisher1936use].
It is a nice dataset because it is reasonably small.
This makes it easy to visualize.
It also makes it a good daata set when trying to learn new analyses, particularly when the data set intende to be analysed is much larger.
It is also a part of R so most intallations should have it.
It can be loaded as follows.


```{r}
data("iris")
```


More information can be found using `?iris`.


We can visualize this data using histograms.


```{r}
library(ggplot2)
library(reshape2)
iris2 <- melt(iris)

p <- ggplot(iris2, aes(x=value, fill = Species))
p <- p + geom_histogram(binwidth = 0.2, alpha=.5)
p <- p + facet_grid(. ~ variable, scales = "free")
p <- p + xlab("Length")
p <- p + ylab("Count")
p <- p + theme_bw()
```



```{r}
p
```



# References

